### 2019-05-20 README.Rmd
remove rtools from readme

Windows users install [Rtools](https://cran.r-project.org/bin/windows/Rtools/) first.

@@

@@

```{r downstream}
downstream(as.tsn(154395), db = 'itis', downto = 'species', verbose = FALSE)
```

@@

```{r upstream}
upstream("Pinus contorta", db = 'itis', upto = 'Genus', verbose=FALSE)
```

@@

```{r get_ids}
get_ids(names="Salvelinus fontinalis", db = c('itis', 'ncbi'), verbose=FALSE)
```

>>>>

Windows users install Rtools first.

@@

```{r echo=FALSE}
taxize_options(FALSE, quiet = TRUE)
```

@@

```{r downstream}
downstream(as.tsn(154395), db = 'itis', downto = 'species', mesages = FALSE)
```

@@

```{r upstream}
upstream("Pinus contorta", db = 'itis', upto = 'Genus', mesages = FALSE)
```

@@

```{r get_ids}
get_ids(names="Salvelinus fontinalis", db = c('itis', 'ncbi'), mesages = FALSE)
```
